\PaperTitle

### 2024-05-04 Final_Report/paper.tex
finished lgoistic regression subsection

@@

\subsubsection{K-Nearest Neighbors}
K-Nearest Neighbors (KNN) is a supervised learning model which classifies data points
based on their proximity to a specified number (k) of existing data points.
The implementation process is as followed: 
\begin{enumerate}
  \item \textbf{Optimization and Training}: Prior to training the model, the optimal number of neighbors (k) for the model is identified using K-Fold cross validation. This technique involves dividing the training data into multiple folds and utilizing one fold for testing while the remaining ones are used for training. For every fold, a KNN model is trained with a specified k value and the accuracy (external validation) is calculated. Multiple different k values are tested using this process and the k value that yields the highest average external validation is used in the final model. After the optimal k value is calculated, the model achieved an accuracy of 97\% on the testing data. 
  \item \textbf{Evaluating Model}: In order to assess the effectiveness of the model, an independent dataset containing 2000 packets was collected and evaluated. Having the model evaluate a seperate unseen dataset reveals a more realistic measurement of the accuracy of our model. After evaluating this dataset, the KNN model achieves an accuracy of 77\%.
\end{enumerate}

@@

\subsection{Model Comparison and Evaluation Results}
The results in table \ref{tab:results} show that the neural network achieved the highest accuracy (80\%) and Macro F1 score (0.00). These results mean the model was the most effective at classifying the selected websites based on network packet data.
This displays the neural network is much more effective at representing complex relationships in the data than the other models.

  \begin{table}[!h]
    \begin{center}
    \caption{Accuracy and Macro F1 Scores for Each Model}
    \label{tab:results}
    \begin{tabular}{|c|c|c|}
      \hline
      Model & Accuracy & Macro F1 \\
      \hline
      Logistic Regression & 56\% & 0.00 \\
      K-Nearest Neighbors & 77\% & 0.00 \\
      Random Forest & 78\% & 0.00 \\
      Neural Network & 80\% & 0.00 \\
      \hline
    \end{tabular}
    \end{center}
  \end{table}

>>>>

The Logistic regression was such an ideal choice for our baseline specifically because of its interpretability characteristics. We wanted to pick a model which would $(1)$ allow us the swiftest entry point into our approach and $(2)$ allow for us to not only have a simple foundation but a foundation from which we could improve upon.

The execution of this model was rather simple: splitting the data into training and testing sets and executing a standard regression to be analyzed. This simplistic approach, as previously mentioned, allowed for us to inspect which features were most advantageous for us and more importantly which features we would continue to analyze.

@@

\subsubsection{K-Nearest Neighbors}

@@

\subsection{Model Comparison and Evaluation Results}
